%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1.5, 1 December 2018) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.https://www.overleaf.com/project/5de5c61491f801000160d30b
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.5cm,marginparsep=1.25cm,top=1.0cm,bottom=1.5cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
% If using xelatex or lualatex:
\setmainfont{Carlito}
\else
% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\fi
\usepackage[colorlinks = true,
    linkcolor = grey,
    urlcolor  = grey,
    citecolor = grey,
    anchorcolor = grey]{hyperref}

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{SlateGrey}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
% \addbibresource{sample.bib}

\begin{document}
    \name{Md. Badi-Uz-Zaman Shajib}
    \tagline{Principal Engineer \& Software Developer}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
% \photo{2.5cm}{MyMy}
    \personalinfo{
    % You can add your own with \printinfo{symbol}{detail}

        \email{mbzshajib@gmail.com}
        \phone{+88 01611120220}
        \location{Dhaka, Bangladesh}
        \linkedin{\href{https://www.linkedin.com/in/mbzshajib}{mbzshajib}}
        \github{\href{https://github.com/mbzshajib}{mbzshajib}}
    }

%% Make the header extend all the way to the right, if you want.
    \begin{fullwidth}
        \makecvheader
    \end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
    \AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
% \cvsection[page1sidebar]{About Me}
% Passionate to apply my acquired engineering knowledge and solve critical business and social problems which will add value to society and help people to have a better life.

    \cvsection[page1sidebar]{Experience}

    \cvevent{Principal Engineer}{\href{https://www.bkash.com/}{bKash Limited}}{Nov. 2021 – Present.}{Dhaka, Bangladesh}
    \begin{itemize}
        \item Understand the complex and proprietary payment system of bKash, analyze system bottlenecks of existing architecture.
        \item Working on some legacy services to convert them to reactive architecture for better performance.
    \end{itemize}



    \cvevent{Principal Software Engineer}{\href{https://konasl.com/}{Kona Software Lab Ltd}}{Sept. 2013 – Nov. 2021}{Dhaka, Bangladesh}
    \begin{itemize}
        \item Study, understand and implement specifications on payment and security for development of payment modules.
        \item Worked on the system design team for Kona Pay Platform, NexusPay, DFS, and developed account and payment authorization modules of the core platform. Tuned the modules to scale up to 200 real-time financial transactions per second and 50M transaction per day.
        \item Analyzed client requirements and design them to fit into the product. Worked as tech lead of development team for several projects in planning, developing, and delivering the project requirements within timeline.
        \item Resolved critical production issues to meet the SLA.
    \end{itemize}




    \cvsection{Mentionable Projects}

    \cvevent{
        Digital Financial System (DFS)
    }{
        Java, Spring, Oracle, Hibernate, Redis, RabbitMQ, Micro Services, Batching, Undertow, Nginx, Safenet, APM, ELK, Grafana, Elasticsearch, Prometheus, ISO-8583, ISO-9564, PCI/DSS.
    }{}{
        \href{https://konasl.com/digitization-platform/kona-dfs/}{Digital Financial System}
    }
    The platform provides end consumers a unified digital environment to support a large number of active users to avail payment and other value-added services. Along with other payment services, it supports the USSD channel, virtual card, reward management, promotion, and back-office batch processing, and several web portals to support business.

    \begin{itemize}
        \item Designed and developed core Accounting and Payment modules of the platform.
        \item Monitor system, optimized and tested for performing 20M real-time transactions per day. Tested system with 50M  (1.5M active) users among them.
        \item Improved processing time for back-office transaction reporting, clearing & settlement batch data processing (50M) from 14 to 3.9 hours)
        \item Monitor system performance and optimize for performing 60M transactions per day in RDB.
        \item Designed application deployment architecture for the private data center. Also implemented automatic deployment with Ansible with zero downtime.
    \end{itemize}

% \divider
    \addnextpagesidebar[-1ex]{page2sidebar}



% \divider









    \cvevent{NexusPay}{
        Java, Spring, Hibernate, Oracle, Redis, RabbitMQ, Micro Services, wildfly, HCE, ATM, POS, EMV QR, NFC, Thales HSM, PM, ISO-8583, ISO-9564, PCI/DSS.
    }{}{\href{https://www.dutchbanglabank.com/nexuspay/nexusPay-home.html}{NexusPay}}
    NexusPay is a digitized payment platform for the existing bank accounts, credit/debit cards, Mobile banking, and Agent
    Banking accounts of Dutch-Bangla Bank Ltd, Bangladesh. This project is a customized variant
    of Kona Pay]Platform for Bank Integration.

    \begin{itemize}
        \item Integrated four bank accounting and issuing systems for mobile payment cards.
        \item Support multiple payment & transaction methods (e.g. NFC, POS, HCE, EMV QR, e-com, utility & bill, ATM etc.)
        \item Worked as a system designer and implemented core authorization modules and POS applications on Ingenico and Nexgo devices for contactless payment.
        \item Guided a team consisting of 18 programmers.
        \item Prepared app servers and deployed in Bank data center with compliance of regulatory, high availability, and option to scale up.
    \end{itemize}

% \divider







    \cvevent{Kona Card}{
        Java, Spring, Hibernate, Oracle, Redis, RabbitMQ, Micro Services HCE, HSM, ISO-8583, ISO-9564.
    }{}{\href{https://www.konacard.co.kr}{Kona Card}}
    Kona Card is a prepaid card service, popular in South Korea. It has been designed on HCE-based tokenization platform KonaPay, enabled secured payment in smartphones, POS, ATM, web, smart-card, and other flexible channels.
    \begin{itemize}
        \item Design & developed User Management and Remote Payment Gateway module of this core platform. Also, took part in the architecture designing of core KonaPay modules.
        \item Developed a continuous delivery process with Jenkins and Oracle Virtual box.
    \end{itemize}

% \divider






    \cvevent{EMV Verification Tool}{Java, SmartCard, Payment Card, EMV, VISA, MASTERCARD, AMEX, ISO-7816. }{}{\href{https://konasl.com/smart-card-and-personalization/emv-verification-tool-k-evt}{emv-verification-tool-k-evt}}
    Tool to test personalized Payment(EMV) cards before issuing to users if different data and security module is working according to the specifications of payment brands( e.g. VISA, MASTERCARD, AMEX, etc.)
    \begin{itemize}
        \item Studied specifications, designed and developed, tested, implemented reporting modules to support new payment brands.
    \end{itemize}

% \divider







    \cvevent{Instant Issuance Service}{Java, SmartCard, Payment Card, Hoodo, EMV, VISA, MASTERCARD, AMEX, KonaCard ISO-7816.}{}{\href{https://konasl.com/smart-card-and-personalization/instant-issuance-system-k-iis}{smart-card-and-personalization/instant-issuance-system-k-iis}}
    Desktop application aimed to customize and issue payment cards to customers at the bank branch at once.
    \begin{itemize}
        \item Study specifications, design, and develop to support new payment brands.
        \item Integrated Hoodo machine.
    \end{itemize}



% \cvevent{Key Management System}{Spring, MyBatis, MySQL, Oracle, HSM, Safenet, Thales, PKCS11.}{}{}
% To perform cryptographic operation securely, HSM (Hardware Security Module) is used, which is accessed by KMS through simple generic APIs hiding hardware complexities.
% \begin{itemize}
%     \item Worked on customization of the module and HSM integration.
% \end{itemize}



    \cvsection{Volunteer Project}

    \cvevent{DHAKA NEXT}{PHP, MYSQL, Laravel, Wearable.}{}{\href{https://next.dhakarunlords.com}{next.dhakarunlords.com}}
    DHAKA NEXT platform replaces the standard physical race with a virtual one to empower active and aspiring athletes to maintain their fitness even in Covid-19.

    \begin{itemize}
        \item Consulted to design and integrate race platform with fitness data provider (Strava, MapMyRun). Throttled third-party paid API calls to reduce cost.
        \item Defined race policy services and consulted for server load maintenance at race time.
        \item Designed, Tested, and optimized system for 5K people to participate in a single race.
    \end{itemize}




% \divider





% \cvevent{Key Management System }{Spring, MyBatis, MySQL, Oracle, HSM, Safenet, Thales.}{}{}
% To perform cryptographic operation securely, HSM (Hardware Security Module) is used, that is accessed by KMS through simple generic APIs hiding hardware complexities.
% \begin{itemize}
%     \item Worked on customization of the module and HSM integration.
% \end{itemize}

% \divider






% \cvevent{Technical Expertise }{Programming Languages}{}{}
% \begin{itemize}
% \item HTML/CSS \ (3yrs+)					
% \item JAVASCRIPT \ (2yrs+)
% \item PYTHON \& R  (4yrs+)
% \item C++ \ (2yrs+)
% \item SQL/MYSQL/NoSQL\ (2yrs+)
% \item SPSS/STATA \ (2yrs+)
% \item Artificial Intelligence: Machine Learning/Deep Learning/Robotics \ (1yr+)
% \end{itemize}
% \cvevent{Product Manager \& UI Lead}{Google}{Oct 2001 -- July 2005}{Palo Alto, CA}

% \begin{itemize}
% \item Appointed by the founder Larry Page in 2001 to lead the Product Management and User Interaction teams
% \item Optimized Google's homepage and A/B tested every minor detail to increase usability (incl.~spacing between words, % color schemes and pixel-by-pixel element alignment)
% \end{itemize}
%
% \divider

% \cvevent{Product Engineer}{Google}{23 June 1999 -- 2001}{Palo Alto, CA}

% \begin{itemize}
% \item Joined the company as employe \#20 and female employee \#1
% \item Developed targeted advertisement in order to use user's search queries and show them related ads
% \end{itemize}
% \cvsection{A Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% Some ad-hoc tweaking to adjust the labels so that they don't overlap
% \wheelchart{1.5cm}{0.5cm}{%
%   25/10em/accent!30/\footnotesize\\[1ex]Sleeping \& dreaming about work,
%   20/9em/accent!60/\footnotesize\\[1ex]Spending time with family,
%   5/13em/accent!10/\footnotesize\\[1ex]Hobbies,
%   20/15em/accent!40/\footnotesize\\[1ex]Working with stakeholders to define smooth business continuity,
%   30/10em/accent/\footnotesize\\[1ex]Overseeing provision of end-user services\, including help desk and technical support services,
%   5/8em/accent!20/\footnotesize\\[1ex]Planning out task for upcoming day
% }

% \clearpage

% \cvsection[page2sidebar]{}
% 
% \nocite{*}
% 
% \printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]
% 
% \divider
% 
% \printbibliography[heading=pubtype,title={\printinfo{\faFileTextO}{Journal Articles}}, type=article]
% 
% \divider
% 
% \printbibliography[heading=pubtype,title={\printinfo{\faGroup}{Conference Proceedings}},type=inproceedings]
% 
%% If the NEXT page doesn't start with a \cvsection but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}

\end{document}



% \cvsection[page2sidebar]{Education}
% \begin{itemize}
% \item \cvevent{B.Sc.\ in Mathematics}{Lagos State University}{2017 -- 2021}{}
% \item \cvevent{NCE in Chemistry/Mathematics}{ADENIRAN OGUNSANYA COLLEGE of EDUCATION}{2009 -- 2012}{}
% \item \cvevent{IGANDO COMMUNITY HIGH SCHOOL}{2000 -- 2005}{}
% \item \cvevent{IGANDO PRIMARY SCHOOL LGA}{1995 -- 1999}{}

% \end{itemize}