%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[
  pdfpagelabels=true,
  pdftitle={CV of Shajib},
  pdfauthor={Md. Badi Uz Zaman Shajib},
]{hyperref}
\usepackage{bookmark}
\usepackage[scale=0.90]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{2cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{13cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------










\firstname{Md Badi Uz Zaman Shajib}
\familyname{}
\title{Software Engineer}         
\address{}{Dhaka, Bangladesh}   
\mobile{ +88 016 111 20220}    
%\phone{}                
%\fax{Votre Fax}                      
\email{mbzshajib@gmail.com}                              
\extrainfo{\href{https://www.linkedin.com/in/mbzshajib/}{LinkedIn}, \href{https://github.com/mbzshajib}{GitHub}}
% \extrainfo{}
% \photo[50pt]{photo.png} 
% \quote{
% Passionate to apply my acquired engineering knowledge and solve critical business and social problems which will add value to society and help people to have a better life
% }
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\usepackage{multibib}
% \newcites{book,misc}{{Books},{Others}}

\nopagenumbers{}                         
\begin{document}
\maketitle
\section{Summary}
\cvline{}{
Passionate to apply my acquired engineering knowledge and solve critical business and social problems which will add value to society and help people to have a better life.
}

  
  
  


\section{Technical Skills}
\cvline{Languages \& Frameworks}{Java, C, Spring Framework, Spring Boot, Spring Batch, Spring Cloud, JPA, Hibernate, SQL(Oracle \& MySQL), NoSQL(DynamoDB), Shell Script.}

\cvline{Technology \& Tools}{Redis, RabbitMQ, Kafka, Tomcat, Undertow, HA Proxy, Mosquitto, Zuul, F5, Switch, JMeter, ELK Stack, APM, Prometheus, Grafana, Unix/Linux, Gradle, Maven, Docker, Git, Jenkins, Ansible, Jira, Confluence, Intellij IDEA, Visual Studio.}

\cvline{Payment \& Security}{EMV Payment, Smart Card, Tokenization, HCE Payment, QR Payment, Payment Gateway, Payment Switch, HSM, Cryptography, POS, Accounting, ISO/IEC-7816, ISO-8583, PCI/DSS, ISO 9564, PKCS7, PKCS11.}

\cvline{Interest}{Software Design, Micro Service, Cloud Computing.}

\section{Projects}

\cventry{\textbf{DFS}}
{Digital Financial System}
{}
{Reference: \href{https://konasl.com/digitization-platform/kona-dfs/}{Digital Financial System}}
{\href{https://nagad.com.bd}{nagad.com.bd}}
{ A flexible product based on Kona Pay Platform to serve the business to provide its customer a unified digital payment platform to support large number of active users who perform payment and other value added services. Along with other Kona Pay services it supports USSD channel, virtual card payment, reward management, back office batch processing and several web portals to serve business.}

 \cvline{}{
  \begin{itemize}
    \item Support 50M users and 3.5M realtime transaction(daily avg) in Nagad Project (DFS Deployment), which is the fastest growing MFS in Bangladesh.
    \item Worked on batch data processing for back office transaction clearing \& settlement, reporting and data warehousing.
    \item Monitor system performance and optimized for performing 60M transactions per day.
    \item Deployed on private data center ensuring compliance of regulatory, security, high availability, and options to scale up.
    \item I have worked as a System Designer and tech lead of the core system team. Designed and developed core Accounting and Payment services of the platform.
    \item \textbf{Java, Spring Boot, Spring Batch, Spring Cloud, Hibernate, Oracle, HA Proxy, Nginx, HCE, ISO 8583, Accounting System, EMV QR, Payment Processor, F5, Safenet HSM, Redis, RabbitMQ, APM, ELK, Grafana, Prometheus. }
  \end{itemize}
  }




% \cvline{}{}
\cventry{\textbf{DHAKA NEXT}}
{DHAKA NEXT}
{}
{Reference: \href{https://next.dhakarunlords.com}{next.dhakarunlords.com}}
{}
{DHAKA NEXT platform to replace the standard physical race with a virtual one to empower active and aspiring athletes to maintain their fitness even in the times of Covid-19.}

 \cvline{}{
  \begin{itemize}
    \item Worked as system designer to integrate race platform with fitness data provider (Strava, MapMyRun) Throttled third-party paid API calls to reduce cost.
    \item Designed race policy and consulted for server load maintenance at race time.
    \item Designed, Tested, and optimized system for 5K people to participate in a single race.
    \item \textbf{PHP, MYSQL, Laravel, Wearable. }
   \end{itemize}
  }



% \cvline{}{}
\cventry{\textbf{NexusPay}}
{NexusPay}
{}
{Reference: \href{https://www.dutchbanglabank.com/nexuspay/nexusPay-home.html}{NexusPay}}
{}
{NexusPay is a digitized payment platform for the existing bank accounts, credit/debit cards, Mobile banking, and Agent Banking accounts of Dutch-Bangla Bank Ltd, Bangladesh. This project is a customized variant of \href{https://konasl.com/digitization-platform/kona-pay/}{Kona Pay} Platform for Bank Integration.}
 \cvline{}{
  \begin{itemize}
    \item Integrated multiple bank accounting systems for issuing HCE payment card.
    \item Support multiple payment \& transaction methods (e.g. NFC, POS, HCE, QR, e-com, utility \& bill, ATM etc.)
    \item Worked as a system designer and implemented core payment authorization modules and POS applications on Ingenico and Nexgo devices for contactless payment.
    \item Prepared app servers and deployed in Bank data center with compliance of regulatory, high availability, and option to scale up.
    \item \textbf{SpringBoot, Hibernate, Oracle, Redis, RabbitMQ, HCE, Oracle VM, System Automation, Micro Service, PKCS11,
ISO 8583, ISO 9564, Oracle VM}
 \end{itemize}
  }







% \cvline{}{}
\cventry{\textbf{Kona Card}}
{Kona Card}
{}
{Reference: \href{https://www.konacard.co.kr}{Kona Card}}
{}
{Kona Card is a prepaid card service, popular in South Korea. It has designed on HCE based tokenization platform \href{https://konasl.com/digitization-platform/kona-pay/}{Kona Pay}, enabled secured payment in smartphones, POS, ATM, web, smart-card, and other flexible channels.}
 \cvline{}{
  \begin{itemize}
    \item Design \& developed User Management and Remote Payment Gateway module of this core platfrom. Also, took part in architecture designing of core KonaPay modules.
    \item Developed a continuous delivery process with Jenkins and Oracle Virtual box.
    \item \textbf{SpringBoot, Hibernate, Oracle, Redis, RabbitMQ, HCE, Oracle VM, System Automation, Micro Service, PKCS11, ISO 8583, ISO 9564, Oracle VM.}
  \end{itemize}
  }
 






  





% \cvline{}{}
\cventry{\textbf{IIS}}
{Instant Issuance Service}
{}
{Reference: \href{https://konasl.com/smart-card-and-personalization/instant-issuance-system-k-iis}{smart-card-and-personalization/instant-issuance-system-k-iis}}
{}
{Desktop application aimed to customize and issue payment cards to customers at bank branch at once.}

 \cvline{}{
  \begin{itemize}
    \item Study specifications, design and develop to support new payment brands.
    \item Integrated Hoodo machine.
    \item \textbf{Java, SmartCard, Payment Card, Hoodo, EMV, VISA, MASTERCARD, AMEX, ISO-7816. }
  \end{itemize}
  }
  



% \cvline{}{}
\cventry{\textbf{KMS}}
{Key Management System}
{}
{}
{}
{
To perform cryptographic operation securely, HSM (Hardware Security Module) is used, that is accessed by KMS through simple generic APIs hiding hardware complexities.
}
 \cvline{}{
  \begin{itemize}
    \item Worked on customization of the module and HSM integration.
    \item \textbf{Spring, MyBatis, MySQL, Oracle, HSM, Safenet, Thales.}
  \end{itemize}
  }
  








\section{Experience}
  
  
  \cventry{Nov. 2021 – Present.}{Principal Engineer}{\href{https://www.bkash.com/}{bKash Limited}}{Dhaka, Bangladesh}{}{}{}
  \cvline{}{
  \begin{itemize}
      \item Understand the complex and proprietary payment system of bKash, analyze system bottlenecks of existing architecture.
      \item Working on some legacy services to convert them to reactive architecture for better performance.
  \end{itemize}
  }
  
  
  \cventry{Sept. 2013 – Nov. 2021}{Principal Software Engineer}{\href{https://konasl.com/}{Kona Software Lab Ltd}}{Dhaka, Bangladesh}{}{}{}
  \cvline{}{
  \begin{itemize}
      \item Study, understand and implement specifications on payment and security for development of payment modules.
      \item Worked on the system design team for Kona Pay Platform, NexusPay, DFS, and developed account and payment authorization modules of the core platform. Tuned the modules to scale up to 200 real-time financial transactions per second and 50M transaction per day.
      \item Analyzed client requirements and design them to fit into the product. Worked as tech lead of development team for several projects in planning, developing, and delivering the project requirements within timeline.
      \item Resolved critical production issues to meet the SLA.
  \end{itemize}
  }
  
  
  
  
  
  
  



\section{Education}
\cventry{2013--2015}{MASTER of SCIENCE (M.S)}{Computer Science And Engineering}{\href{https://du.ac.bd/}{University of Dhaka}}{\textit{Bangladesh}}{}
\cventry{2009--2012}{BACHELOR of SCIENCE (B.S)}{Computer Science And Engineering}{\href{https://du.ac.bd/}{University of Dhaka}}{\textit{Bangladesh}}{}


\section{Other Information}
\cvline{Language}{Bangla, English}
\cvline{Hobbies \& Interests}{Photography and Traveling.}

\end{document}